### 2014-11-02 evaluation.tex
edits

\begin{itemize} \item \textbf{LWW register}: A last-write-wins register. \item
\textbf{DynamoDB register}: A integer register that allows eventual and strong
puts and gets, conditional puts, increment and decrement operations. \item
\textbf{Bank account}: Our running example, with savings and current accounts.
\item \textbf{Shopping list}: Collaborative shopping list which allows adding
and deleting items. \item \textbf{Online store}: Models an online store with
shopping cart and dynamically changing item prices. Checkout process verifies
that the custormer only pays the accepted price. \item \textbf{RuBis}: An
ebay-like auction site~\cite{}. \item \textbf{Microblog}: A twitter-like
microblogging site, modelled after Twissandra~\cite{}. \end{itemize}

>>>>

\begin{itemize}

\item \textbf{LWW register}: A last-write-wins register.

\item \textbf{DynamoDB register}: A integer register that allows eventual and
strong puts and gets, conditional puts, increment and decrement operations.

\item \textbf{Bank account}: Our running example, with savings and current
accounts.

\item \textbf{Shopping list}: Collaborative shopping list which allows adding
and deleting items.

\item \textbf{Online store}: Models an online store with shopping cart and
dynamically changing item prices. Checkout process verifies that the custormer
only pays the accepted price. \item \textbf{RuBis}: An ebay-like auction
site~\cite{}.

\item \textbf{Microblog}: A twitter-like microblogging site, modelled after
Twissandra~\cite{}.

\end{itemize}
